\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{color,xcolor}
\usepackage[
pdfauthor={Ou Changkun},
pdftitle={CV},
pdfproducer={Ou Changkun}
pdfcreator={Ou Changkun},
pdfsubject={Ou Changkun CV},
pdfkeywords={CV, Ou Changkun},
]{hyperref}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\definecolor{linkcolor}{HTML}{00008B}
\definecolor{shade}{HTML}{D4D7FE}      %light blue shade
\definecolor{text1}{HTML}{000000}      %text is black
\definecolor{headings}{HTML}{00008B}   %navy blue
\hypersetup{colorlinks,breaklinks,
            urlcolor=linkcolor,
            linkcolor=linkcolor
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{https://changkun.us/}{\Large Ou Changkun}} & \\
Munich, Germany                                          & \\
+49 157 7214 1480                                        & \\
\href{mailto:hi@changkun.us}{hi@changkun.us}             & \\
\href{https://changkun.us/about}{changkun.us/about}      & \\
\sffamily Last update: \today                            & \\
\end{tabular*}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Munich (LMU)}{Munich, Germany}
      {Master of Science in Human-Computer Interaction}{since Oct. 2016}
    % \resumeSubheading
    %   {University of Electronic Science and Technology of China (UESTC)}{Chengdu, China}
    %   {Master of Engineering in Big Data}{Aug. 2016 -- Paused at Oct. 2016}
    \resumeSubheading
      {University of Munich}{Munich, Germany}
      {Exchange Student in Media Informatics}{Sep. 2015 -- Feb. 2016}
    \resumeSubheading
      {Southwest University for Nationalities (SWUN)}{Chengdu, China}
      {Bachelor of Engineering in Computer Science;  GPA: 3.74/4.0 (1/154)}{Sep. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://magiclingua.com/}{MagicLingua}}{Munich, Germany}
      {Fullstack Development (Praktikum)}{Apr. 2017 -- Aug. 2017}
      \resumeItemListStart
        \resumeItem{alexa-skill}
          {Developed voice interaction interface for English learner based on Amazon Alexa.}
    \resumeItemListEnd
    \resumeSubheading
      {\href{https://shiyanlou.com/}{Shiyanlou}}{Chengdu, China}
      {Software Engineer (Intern)}{Jun. 2016 -- Sep. 2016}
      \resumeItemListStart
        \resumeItem{shiyanlou-logsys}
          {Built \& maintained ELK+Redis distributed log analytics system;}
        \resumeItem{shiyanlou-desktop}
          {Developed a cross-platform Electron Windows/macOS/Linux desktop client;}
        \resumeItem{shiyanlou-recosys}
          {Developed a course recommendation system based on collaborative filtering through Python;}
        \resumeItem{shiyanlou-courses}
          {Wrote 17 crash and advanced tutorials for C++ users.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{http://www.medien.ifi.lmu.de}{LMU Media Informatics Group}}{Munich, Germany}
      {Student Research Internship}{Oct. 2016 -- Jan. 2016}
      \resumeItemListStart
        \resumeItem{Research topics}
          {Combining motion sensors and touch offset classify hand Posture and users}
        \resumeItem{Prototyping development}
          {Developed a iOS prototype App for User Study, and finished densely data analysis via Machinea Learning algorithm}
        \resumeItem{Paper report}
          {Finished a report to summarize and conclude all discovering}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UniWorX Monitor}{Munich, Germany}
      {Personal Project}{Mar. 2017}
      \resumeItemListStart
        \resumeItem{Tech Stack}
          {Python, Polymer, Node.js Express, Electron}
        \resumeItem{Description}{Developed an unofficial better LMU UniWorX System with new courses notifications}
      \resumeItemListEnd

    \resumeSubheading
      {Munich Renting Tool}{Munich, Germany}
      {Personal Project}{Oct. 2016}
      \resumeItemListStart
        \resumeItem{Tech Stack}
          {JavaScript, Python, Google Map API, BeautifulSoup4}
        \resumeItem{Description}{A location visualization tool for Munich Studentenwerk private savings}
      \resumeItemListEnd

    \resumeSubheading
      {Designing Alternative Contact-free Control Modalities for Smart Watches}{Chengdu, China}
      {Bachelor Thesis}{Apr.2016 -- Jun.2016}
      \resumeItemListStart
        \resumeItem{Tech Stack}
          {Swift, Node.js, Web Socket, watchOS, iOS, Leap Motion, Git}
        \resumeItem{Description}{Developed an alternative way -- midair gesture control -- to operate smart watches}
      \resumeItemListEnd

    \resumeSubheading
      {Implementation of Interaction Perception Center}{Chengdu, China}
      {SWUN National Student-Innovative Project at SWUN Guigu Lab}{Apr. 2014 -- Apr. 2015}
      \resumeItemListStart
        \resumeItem{Responsibility}
          {Team leader and development}
      \resumeItemListEnd

    \resumeSubheading
      {Research on Spetical Interaction}{Chengdu, China}
      {SWUN Normal Student-Innovative Project at SWUN Computer Vision Lab}{Jun. 2013 -- Dec. 2013}
      \resumeItemListStart
        \resumeItem{responsibility}
          {Team leader and development}
      \resumeItemListEnd

    \resumeSubItem{More Open Source Projects}
      {\href{https://github.com/changkun/}{github.com/changkun}}

  \resumeSubHeadingListEnd
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages:}{ python; javascript; c; c++; obj-c; swift; markdown/pandoc; \LaTeX; Native Chinese Speaker; Professional Fluent English; Elementary German}
   }
   \item{
    \textbf{Systems/Tools:}{ Mac user; General Linux DevOps; Docker; AWS/DigitalOcean/Aliyun; SQL/MongoDB; zsh/tmux/vim/vscode}
   }
   \item{
    \textbf{Frameworks:}{ numpy/opencv/matplotlib/skearn/tensorflow, flask, jquery/react/vue/polymer/electron, node/express}
   }
   \item{
     \textbf{Knowledges:}{ 
       \resumeItemListStart
        \resumeItem{Human Side}
          { Human-Computer Interaction; User Study; User Experience; Product Prototyping; Human Computation; Social Psychology}
        \resumeItem{Machine Side}
          { Machine Learning; Recommendation System; Big Data Mining; Computer Vision; Distributed Computing; Compiler Technique; System Architecture}
        \resumeItem{Mathematics}
          { Functional Analysis; Stochastic Process; Analytic Number Theory; Formal Logic and Proof}
      \resumeItemListEnd
     }
   }
 \resumeSubHeadingListEnd
\section{Publications}
 \resumeSubHeadingListStart
    \item{
      Matthias Geiger, Changkun Ou, Cedric Quintes.
      \emph{WatchOut: A Road Safety Extension for Pedestrians on a Public Windshield Display}.
      Lercture Advanced Topics in HCI, IFI LMU, 2017. In Proceedings.
    }
    \item{
      Changkun Ou, Yifei Zhan, Zhe Li.
      \emph{A Novel GWAP Disaster Monitoring System}.
      Lercture Human Computation, IFI LMU, 2017.
      \href{https://github.com/changkun/hc-ss17-disaster-monitoring/blob/master/report/hc_final_project_report_team_Hotpot.pdf}{English}
    }
   \item{
       Changkun Ou.
       The Fastest Guide of C++11/14. 
       2016, 
       \href{https://www.gitbook.com/book/changkun/cpp1x-tutorial/details}{Simplified Chinese}, 
       \href{https://github.com/changkun/cpp1x-tutorial}{Source Code}
   }
   \item{
       Changkun Ou, Yaxi Chen(responsible professor), Andreas Butz(co-reviwer).
       Designing Alternative Contact-free Control Modalities for Smart Watches. 
       2016, Bachelor Thesis. \href{https://changkun.us/files/cv/bachelor-thesis-cn.html}{Simplified Chinese}, 
       \href{https://changkun.us/files/cv/bachelor-thesis-en.html}{English}
   }
   \item{
       Changkun Ou.
       Mathematical Modeling Tutorial (Mandarin Chinese Video Series.
       2016, \href{https://www.youtube.com/watch?v=EUfXE3vP9_A&list=PLwUqqMt5en7c7iZIseCVAS5BX6RPkS-qR}{YouTube Playlist}
   }
   \item{
       Changkun Ou, Yaxi Chen. 
       Combining Touch Biometrics and Motion Sensors for Hand Posture Recognition and User Authentication System. 
       Journal of Southwest University for Nationalities(Nature Science Edition). 
       2016, 42(4):429-435. \href{https://changkun.us/files/cv/touch.swun.html}{Simplified Chinese}
   }
   \item{
       Changkun Ou, Zhaoyang Guo, Yaxi Chen.
       Space interactions based on monocular vision and simple gestures. 
       Journal of Southwest University for Nationalities(Natural Science Edition). 
       2014, 40(16):871-876. \href{https://changkun.us/files/cv/vision.swun.html}{Simplified Chinese}
   }
   \item{
       Changkun Ou, Mu Huang, Mengxin Shi, Jiang Cheng. 
       A Study in Keep-Right-Except-To-Pass Rule. 
       2014, MCM Meritorious Winner \href{https://changkun.us/files/cv/28922.public.html}{English}
   }
 \resumeSubHeadingListEnd
\section{Honors \& Awards}
  \resumeSubHeadingListStart
    \resumeSubheading
        {App@Night 2016 hackthon at University of Munich}{Munich, Germany}
        {IBM IoT team Successful Participant}{Nov. 2016}
    \resumeSubheading
        {hackaTUM at Technical University of Munich}{Munich, Germany}
        {Landeshauptstadt Muenchen Successful Participant}{Nov. 2016}
    \resumeSubheading
        {China National Scholarship}{Chengdu, China}
        {At UESTC}{Sep. 2016}
    \resumeSubheading
        {SWUN Bachelor Graduation Thesis Award}{Chengdu, China}
        {Excellent Thesis}{Jun. 2016}
    \resumeSubheading
        {Sichuan Province University Graduates Award}{Chengdu, China}
        {Outstanding Student}{Jan. 2016}
    \resumeSubheading
        {First-class Scholarship}{Chengdu, China}
        {SWUN Outstanding Student}{Nov. 2015}
    \resumeSubheading
        {SWUN College Student-Innovative Activity 2014}{Chengdu, China}
        {Annual Excellent Project}{Jun. 2015}
    \resumeSubheading
        {The National College Student-Innovative Projects}{Chengdu, China}
        {Concluding Certificate}{Jun. 2015}
    \resumeSubheading
        {Sichuan Computer Production Competition}{Chengdu, China}
        {2nd Award}{May 2015}
    \resumeSubheading
        {First-class Scholarship}{Chengdu, China}
        {SWUN Outstanding Student}{Nov. 2014}
    \resumeSubheading
        {China National Scholarship}{Chengdu, China}
        {At SWUN}{Sep. 2014}
    \resumeSubheading
        {Sichuan Computer Production Competition}{Chengdu, China}
        {2nd Award}{Jun. 2014}
    \resumeSubheading
        {Mathematical Contest in Modeling(MCM) 2014}{Chengdu, China}
        {Meritorious Winner}{Apr. 2014}
    \resumeSubheading
        {First-class Scholarship}{Chengdu, China}
        {SWUN Outstanding Student}{Nov. 2013}
    \resumeSubheading
        {Mathematical Contest in Modeling(MCM) 2013}{Chengdu, China}
        {Successful Participant}{Apr. 2013}
  \resumeSubHeadingListEnd

\section{Selected Public Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Juejin Translation Project}{\href{https://github.com/xitu/gold-miner}{GitHub}}
      {Translator, articles translation from English to Chinese}{since Apr. 2017}
      \resumeItemListStart
        \resumeItem{Translation}
          {\href{https://juejin.im/post/5937a61f2f301e006b2879a9}{How to build complex user interfaces without going completely insane}}
        \resumeItem{Proofreading}
          {\href{https://github.com/xitu/gold-miner/pull/1603}{Everyone is a designer. Get over it.}}
        \resumeItem{Translation}
          {\href{https://juejin.im/post/5915880b570c35006932fac9}{How to pretend you’re a great designer}}
      \resumeItemListEnd
    
    \resumeSubheading
      {Personal Translation}{}
      {Translation from English to Chinese}{since May 2016}
      \resumeItemListStart
        \resumeItem{\href{https://github.com/changkun/LeapDocCN}{Leap Motion Official Development Documentation Translation}}
          {full translation}
        \resumeItem{\href{http://swift.gg/2016/05/18/api-design-guidelines/}{Swift 3 API Design Guidelines}}
          {full translation}
        \resumeItem{\href{https://github.com/numbbbbb/the-swift-programming-language-in-chinese}{The Swift Programming Language Chinese Translation}}
          {responsible for Release Changes chapter}
      \resumeItemListEnd

    \resumeSubheading
        {Academic Tutor}{Chengdu, China}
        {Cooperation lecture “Human-Computer Interaction I” between LMU and SWUN}{Jul. 2015}

    \resumeSubheading
        {Student Volunteer}{Chengdu, China}
        {for Conference Smart Graphics 2015}{Aug. 2015}

    \resumeSubheading
        {SWUN Guigu Lab Team Leader}{Chengdu, China}
        {Tutorial for members applying projects}{Sep. 2014 -- Jun. 2015}

    \resumeSubheading
        {Mathematical Modeling Association Academic Vice Director}{Chengdu, China}
        {Academic tutorial for new members}{Oct. 2012 -- Jun. 2014}

    \resumeSubheading
        {Computer Application and Development Association Core Member}{Chengdu, China}
        {Programming tutorial for new members}{Oct. 2012 -- Dec. 2013}

    \resumeSubheading
        {SWUN Organization federation Excutive Member}{Chengdu, China}
        {Design \& Organization}{Oct. 2012 -- Jun. 2013}
  \resumeSubHeadingListEnd
\end{document}