\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color,xcolor}
\usepackage[
pdfauthor={Ou Changkun},
pdftitle={Resume},
pdfproducer={Ou Changkun}
pdfcreator={Ou Changkun},
pdfsubject={Ou Changkun Resume},
pdfkeywords={Resume, Ou Changkun},
]{hyperref}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\definecolor{linkcolor}{HTML}{00008B}
\definecolor{shade}{HTML}{D4D7FE}      %light blue shade
\definecolor{text1}{HTML}{000000}      %text is black
\definecolor{headings}{HTML}{00008B}   %navy blue
\hypersetup{colorlinks,breaklinks,
            urlcolor=linkcolor,
            linkcolor=linkcolor
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\usepackage{fancyhdr} 
\usepackage{lastpage}
\fancyhf{}
\cfoot{\thepage\ of \pageref{LastPage}}
\pagestyle{fancy}  

\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{https://changkun.us/}{\Large Ou Changkun}} & +49 157 7214 1480 / +86 186 1322 5636\\
Munich, Germany                                      &  \href{mailto:hi@changkun.us}{hi@changkun.us}\\
\sffamily Last update: \today                           & \href{https://changkun.us/about}{changkun.us/about}
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Munich}{Munich, Germany}
      {Master of Science in Human-Computer Interaction}{Oct. 2016 -- Present}
    \resumeSubheading
      {Southwest University for Nationalities}{Chengdu, China}
      {Bachelor of Engineering in Computer Science;  GPA: 3.74/4.0 (1/154)}{Sep. 2012 -- Jun. 2016}
    \resumeSubheading
      {COURSERA}{MOOC platform}
      {Andrew Ng: Deep Learning Specializations, certificates:
       \href{https://www.coursera.org/account/accomplishments/verify/YH4NT7HHN263}{1}, 
       \href{https://www.coursera.org/account/accomplishments/verify/QGH3GNGF6BM4}{2}, 
       \href{https://www.coursera.org/account/accomplishments/verify/6VU45R2SZEF6}{3}}
      {Oct. 2017}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://magiclingua.com/}{MagicLingua}}{Munich, Germany}
      {Fullstack Development (Praktikum)}{Apr. 2017 -- Aug. 2017}
      \resumeItemListStart
        \resumeItem{Voice Assistant}
          {Conversational Design; Nature Language Processing; Backend development; AWS serverless \& DynamoDB}
    \resumeItemListEnd
    \resumeSubheading
      {\href{https://shiyanlou.com/}{Shiyanlou}}{Chengdu, China}
      {Software Engineer (Intern)}{Jun. 2016 -- Sep. 2016}
      \resumeItemListStart
        \resumeItem{Distributed log system}
          {Distributed log system maintainer; ELK+Redis tech stack}
        \resumeItem{Desktop Client}
          {Cross-platform desktop client development; Electron based}
        \resumeItem{Recommendation system}
          {Course recommendation system based; Python wirtten}
        \resumeItem{Wirtten courses}
          {17 written tutorials for C++ users}
    \resumeItemListEnd
    \resumeSubheading
      {\href{http://www.medien.ifi.lmu.de}{LMU Media Informatics Group}}{Munich, Germany}
      {Student Research Internship}{Oct. 2016 -- Jan. 2016}
      \resumeItemListStart
        \resumeItem{Research topics}
          {Combining motion sensors and touch offset classify hand Posture and users}
        \resumeItem{Works}
          {iOS prototyping; Machine Learning based appraoch; paper reporting}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Open Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Open Source Projects}
      {\href{https://github.com/changkun/}{github.com/changkun}}
    \resumeSubItem{Translation Works}
      {\href{https://github.com/changkun/translation}{github.com/changkun/translation}}
  \resumeSubHeadingListEnd
%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages:}{ 
      \textbf{python}; \textbf{javascript}; 
      c; \textbf{c++}; obj-c; swift; 
      \textbf{markdown}/pandoc; \LaTeX; 
      Native Chinese Speaker; Professional Fluent English; Elementary German
     }
   }
   \item{
    \textbf{Systems/Tools:}{ 
      \textbf{macOS} user; General \textbf{Linux DevOps}; \textbf{serverless};
      \textbf{Docker}; AWS/DigitalOcean/Aliyun; 
      RESTful/GraphQL;
      SQL/\textbf{MongoDB}/Redis; 
      zsh/tmux/vim/vscode; 
      PS/PR/AE/AU
    }
   }
   \item{
    \textbf{Frameworks:}{ 
      \textbf{numpy}/\textbf{opencv}/matplotlib/\textbf{skearn}/\textbf{tensorflow}/\textbf{keras}, 
      flask/django, 
      \textbf{jquery}/\textbf{angular}/polymer/\textbf{electron}, 
      \textbf{node}/express
    }
   }
   \item{
     \textbf{Knowledge:}{ 
       \resumeItemListStart
        \resumeItem{Machine Side}
        { 
          \textbf{Machine Learning; Deep Learning};
          Recommendation System; 
          \textbf{Data Mining}; 
          \textbf{Computer Vision}; 
          Distributed Computing; 
          Compiler Technique; 
          System Architecture
        }
        \resumeItem{Human Side}
          { 
            \textbf{Human-Computer Interaction}; 
            User Study; 
            User Experience Design; 
            Product Design; 
            Human Computation; 
            Social Psychology
          }
        \resumeItem{Mathematics}
          { 
            Functional Analysis; 
            \textbf{Stochastic Process}; 
            Analytic Number Theory; 
            Formal Logic and Proof
          }
      \resumeItemListEnd
     }
   }
 \resumeSubHeadingListEnd
%--------PUBLICATIONS------------
\section{Publications}
 \resumeSubHeadingListStart
   \item{
    Matthias Geiger, Changkun Ou, Cedric Quintes.
     \emph{WatchOut: A Road Safety Extension for Pedestrians on a Public Windshield Display}.
     Lercture Advanced Topics in HCI, IFI LMU, 2017. \href{https://github.com/changkun/ath-windshild-display/blob/master/paper/ath.pdf}{English}.
   }
   \item{
     Changkun Ou, Yifei Zhan, Zhe Li.
     \emph{A Novel GWAP Disaster Monitoring System}.
     Lercture Human Computation, IFI LMU, 2017.
     \href{https://github.com/changkun/hc-ss17-disaster-monitoring/blob/master/report/hc_final_project_report_team_Hotpot.pdf}{English}
   }
   \item{
       Changkun Ou.
       \emph{The Fastest Guide of C++11/14}. 
       2016.
       \href{https://www.gitbook.com/book/changkun/cpp1x-tutorial/details}{Simplified Chinese}, 
       \href{https://github.com/changkun/cpp1x-tutorial}{Source Code}
   }
   \item{
       Changkun Ou, Yaxi Chen(responsible professor), Andreas Butz(co-reviwer).
       \emph{Designing Alternative Contact-free Control Modalities for Smart Watches}. 
       Bachelor Thesis. 2016. \href{https://changkun.us/files/cv/bachelor-thesis-cn.html}{Simplified Chinese}, 
       \href{https://changkun.us/files/cv/bachelor-thesis-en.html}{English}
   }
   \item{
       Changkun Ou.
       \emph{Mathematical Modeling Tutorial (Mandarin Chinese Video Series)}.
       2016. \href{https://www.youtube.com/watch?v=EUfXE3vP9_A&list=PLwUqqMt5en7c7iZIseCVAS5BX6RPkS-qR}{YouTube Playlist}
   }
   \item{
       Changkun Ou, Yaxi Chen. 
       \emph{Combining Touch Biometrics and Motion Sensors for Hand Posture Recognition and User Authentication System}. 
       Journal of Southwest University for Nationalities (Nature Science Edition). 
       2016, 42(4):429-435. \href{https://changkun.us/files/cv/touch.swun.html}{Simplified Chinese}
   }
   \item{
       Changkun Ou, Zhaoyang Guo, Yaxi Chen.
       \emph{Space Interactions based on Monocular Vision and Simple Gestures}. 
       Journal of Southwest University for Nationalities(Natural Science Edition). 
       2014, 40(16):871-876. \href{https://changkun.us/files/cv/vision.swun.html}{Simplified Chinese}
   }
   \item{
       Changkun Ou, Mu Huang, Mengxin Shi, Jiang Cheng. 
       \emph{A Study in Keep-Right-Except-To-Pass Rule}. 
       MCM Meritorious Winner, 2014. \href{https://changkun.us/files/cv/28922.public.html}{English}
   }
 \resumeSubHeadingListEnd
\end{document}