\cvsection{Experience}
\begin{cventries}
	\cventry
    {Student Volunteer}
    {Smart Graphics Conference 2015}
    {China}
    {Aug. 2015}
    {
      %\begin{cvitems}
      %  \item {}
      %\end{cvitems}
    }
    
  	\cventry
    {LMU \& SWUN, Course Tutor}
    {Human Computer Interaction I 2015 Summer Semester}
    {China}
    {Jul. 2015}
    {
      %\begin{cvitems}
      %  \item {}
      %\end{cvitems}
    }
    
  	\cventry
    {SWUN, The National College Student-Innovative Project, Project Leader}
    {Implementation of Interaction Perception Centre Based on Cloud Computing and Machine Learning}
    {C/C++/Python/Objective-C/Swift}
    {Apr. 2014 - Apr. 2015}
    {
      \begin{cvitems}
        \item {Responsible for project planning and system architecture, and the most development work;}
        \item {Developed a Multiplatform framework which is large scale distributed machine learning communication toolkit(HorcruxLib), a traditional machine learning algorithm framework(MLiteKit), and a neural network toolkit(SmartNet);}
        \item {The product joined the Sichuan Computer Production Match and won the Second Award.}
      \end{cvitems}
    }
    
    
  	\cventry
    {Smart Graphics Conference, Cooperation Projects, Major Contributor}
    {Smart Graphics 2015 Conference Website Development}
    {HTML/CSS/JS}
    {Nov. 2014}
    {
      \begin{cvitems}
        \item {Responsible for whole development, visual design and maintenance.}
        \item {Website: http://www.smartgraphics.org/sg15/}
      \end{cvitems}
    }
    
    
  	\cventry
    {SWUN, The College Student-Innovative Project, Project Leader}
    {Research on Spetical Interaction Based on Monocular Vision}
    {C++/MFC/OpenCV}
    {Jun. 2013 - Dec. 2013}
    {
      \begin{cvitems}
        \item {Responsible for planning and system architecture, algorithm design. Mainly responsible for the filter module and recognise module.}
        \item {Published a paper named Space interactions based on monocular vision and simple gestures on Journal of Southwest University for Nationalities (Natural Science Edition).}
      \end{cvitems} 
    }
    
    
    
%  \cventry
%    {Freelance Penetration Tester}
%    {SAMSUNG Electronics}
%    {S.Korea}
%    {Sep. 2013, Mar. 2011 - Oct. 2011}
%    {
%      \begin{cvitems}
%        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%        \item {Conducted penetration testing on SAMSUNG Smart TV.}
%      \end{cvitems}
%      \begin{cvsubentries}
%        \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
%        \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
%      \end{cvsubentries}
%    }
\end{cventries}
