
\ifthenelse{\boolean{en}} {
\section{\textbf{Scholarships and Awards}}
}{
\section{\textbf{奖项与荣誉}}
}
\resumeSubHeadingListStartNoLabel
\ifthenelse{\boolean{en}} {
    \resumeSubheading
        {ACM SIGCHI \href{https://sigchi.org/awards/gary-marsden-travel-awards/}{Gary Marsden Travel Awards}}{Jan. 2023}
        {Full Travel Support}{}
    \resumeSubheading
        {ACM Symposium on Virtual Reality Software and Technology}{Nov. 2022}
        {Best Paper Award}{}
    \resumeSubheading
        {ACM SIGCHI Mensch und Computer}{Sep. 2022}
        {Honorable Mention Award}{}
    \resumeSubheading
        {ACM SIGCHI Special Recognitions (CHI '20)}{Nov. 2019}
        {Outstanding Reviews}{}
    \resumeSubheading
        {Siemens AILab Hackathon}{Nov. 2017}
        {2nd Winner}{Munich, Germany}
    \resumeSubheading
        {China National Scholarship}{Sep. 2016}
        {University of Electronic Science and Technology of China}{Chengdu, China}
    \resumeSubheading
        {Excellent Bachelor Thesis Award}{Jun. 2016}
        {Southwest University for Nationalities}{Chengdu, China}
    \resumeSubheading
        {Best University Graduates Award}{Jan. 2016}
        {Sichuan Province}{Chengdu, China}
    \ifthenelse{\boolean{cv}}{
    \resumeSubheading
        {Outstanding Student Scholarship}{Nov. 2015}
        {Southwest University for Nationalities}{Chengdu, China}
    \resumeSubheading
        {Annual Excellent Student Innovative Project}{Jun. 2015}
        {Southwest University for Nationalities}{Chengdu, China}
    \resumeSubheading
        {Sichuan Province Computer Production Competition}{May 2015}
        {2nd Award}{Chengdu, China}
    }{}
    \resumeSubheading
        {China National Scholarship}{Sep. 2014}
        {Southwest University for Nationalities}{Chengdu, China}
    \resumeSubheading
        {Meritorious Winner in American Mathematical Contest in Modeling (MCM' 14)}{Apr. 2014}
        {Southwest University for Nationalities}{Chengdu, China}
}{
    \resumeSubheading
        {ACM SIGCHI 特殊表彰 (CHI 20)}{2019.11}
        {优秀审稿}{慕尼黑，德国}
    \resumeSubheading
        {西门子 AI 实验室黑客马拉松}{2017.11}
        {二等奖}{慕尼黑, 德国}
    \resumeSubheading
        {国家奖学金}{2016.09}
        {电子科技大学}{成都, 中国}
    \resumeSubheading
        {本科优秀毕业论文}{2016.06}
        {西南民族大学}{成都, 中国}
    \resumeSubheading
        {省优秀毕业生}{2016.01}
        {四川省}{成都, 中国}
    \ifthenelse{\boolean{cv}}{
    \resumeSubheading
        {优秀学生奖学金}{2015.11}
        {西南民族大学}{成都, 中国}
    \resumeSubheading
        {学生创新年度优秀项目}{2015.06}
        {西南民族大学}{成都, 中国}
    \resumeSubheading
        {计算机作品赛}{2015.05}
        {四川省二等奖}{成都, 中国}
    }{}
    \resumeSubheading
        {国家奖学金}{2014.09}
        {西南民族大学}{成都, 中国}
    \resumeSubheading
        {美国数学建模竞赛}{2014.04}
        {一等奖（Meritorious Winner）}{成都, 中国}
}
\resumeSubHeadingListEnd