\section{\textbf{Education}}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Munich (LMU)}{Munich, Germany}
      {Research Fellow in Human-Computer Interaction}{Feb. 2019 -- Present}


  \ifthenelse{\boolean{cv}}{
    \resumeSubheading
      {University of Munich}{Munich, Germany}
      {Master of Science in Computer Science; GPA: 2.05/1.00}{Apr. 2018 -- Present}
  }{}

    \resumeSubheading
      {University of Munich}{Munich, Germany}
      {Master of Science in Human-Computer Interaction; GPA: 1.87/1.00; \href{https://github.com/changkun/resume/blob/master/assets/transcript-master-hci.pdf}{Transcript}}{Oct. 2016 -- Jan. 2019}

  \ifthenelse{\boolean{cv}}{
      \resumeSubheading
      {University of Electronic Science and Technology of China (UESTC)}{Chengdu, China}
      {Master of Engineering in Software Engineering}{Aug. 2016 -- Sep. 2016}
    \resumeSubheading
      {University of Munich}{Munich, Germany}
      {Exchange Student}{Sep. 2015 -- Feb. 2016}
  }{}

    \resumeSubheading
      {Southwest University for Nationalities (SWUN)}{Chengdu, China}
      {Bachelor of Engineering in Computer Science;  GPA: 3.74/4.0; Ranking: 1/154; \href{https://github.com/changkun/resume/blob/master/assets/bachelor-transcript.pdf}{Transcript}}{Sep. 2012 -- Jul. 2016}

  \ifthenelse{\boolean{cv}}{
    \resumeSubheading
      {First Middle School of Zhijiang}{Huaihua, China}
      {Senior Middle School; Taken a university entrance examination (Gaokao)}{Mar. 2010 -- Jul. 2012}
    \resumeSubheading
      {Changsha Foreign Language School}{Changsha, China}
      {Senior Middle School}{Aug. 2009 -- Feb. 2010}
    \resumeSubheading
      {Second Middle School of Zhijiang}{Huaihua, China}
      {Junior Middle School}{Sep.2006 -- Jul.2009}
    \resumeSubheading
      {Chengnan Primary School of Zhijiang}{Huaihua, China}
      {Primary School}{Sep. 2000 -- Jul. 2006}
  }{}

  \resumeSubHeadingListEnd