\ifthenelse{\boolean{en}} {
  \section{\textbf{Open Source Activities and Organizations}}
}{
  \section{\textbf{开源贡献}}
}
\small
\ifthenelse{\boolean{en}} {
  A public \href{https://github-readme-stats.vercel.app/api?username=changkun&include_all_commits=true}{statistics} indicates that I have earned 18.2k+ stars, 14.2k+ total code commits, 30 contributed open source projects. A public contribution \href{https://github.com/gayanvoice/top-github-users/blob/858980e5cb10d1b4c27a24d36ae6547aa0f195cd/markdown/public_contributions/germany.md}{ranking} indicates I am a \textbf{top 200 developer in Germany} or a \textbf{top 100 developer in China}. See \href{https://github.com/changkun}{github.com/changkun} for more authored softwares (including frameworks/tools). Here lists a few selected activities and organizations:
}{
  一份\href{https://github-readme-stats.vercel.app/api?username=changkun&include_all_commits=true}{公开统计}显示我已获得超过 18.2k star，并提交过超过 14.2k 次代码，共贡献过超过 30 个开源项目。另一份\href{https://github.com/gayanvoice/top-github-users/blob/858980e5cb10d1b4c27a24d36ae6547aa0f195cd/markdown/public_contributions/germany.md}{公开的贡献排名}显示我是排名前 200 的德国开发者并是排名前 100 的中国开发者。参见 \href{https://github.com/changkun}{github.com/changkun} 查看更多编写的软件、框架和工具。这里列出了一些开源活动和组织：
}
\ifthenelse{\boolean{en}} {
  \resumeSubHeadingListStart
  \resumeSubItem{\href{http://github.com/golang/go/}{Go} (organization member)}{an open sourced programming language developed by a team at Google, and have approx. \href{https://research.swtch.com/gophercount}{2 million developer users} in the globe. I am one of the official Go organization member (163 people in total), current maintainer of x/mobile repository, active contributor to language runtime and standard library.}
  \resumeSubItem{\href{http://github.com/fyne-io/fyne/}{fyne} (organization member)}{an open sourced cross platform GUI framework written in Go, and I am one of the organization member (12 people in total), mainly contributing to graphics and mobile drivers, performance improvements.}
  \resumeSubItem{\href{https://golang.design}{The golang.design Initiative} (founder)}
  {I created the organization. The organization currently hosts 25 software projects and 6 core members. The organization website have 465k+ page views and 66k+ historical viewers in total since Sep 2020.}
  \resumeSubItem{\href{https://talkgo.org}{The TalkGo community} (organization member)}
  {I am a core member of the organization. The community organizes weekly public tech talks, currently have 6.35k+ subscribers, organized 132 public talks. I contributed 7 talks, and they are one of the most viewed talks.}
  \resumeSubItem{\href{https://github.com/xitu/gold-miner}{Juejin Translation Community} (organization member)}
  {Major contributor, translated 50+ articles from English to Chinese.}
  \resumeSubItem{Occasional contributions}{\href{http://github.com/tensorflow/tensorflow/}{Tensorflow} (164+ stars), \href{https://github.com/etcd-io/etcd}{etcd} (39.6k+ stars), etc.}
  \resumeSubHeadingListEnd
}{
  \resumeSubHeadingListStart
  \resumeSubItem{\href{http://github.com/golang/go/}{Go}（组织成员）}{Go 语言是一门由来自 Google 的一个开发者团队推出的编程语言，在全球拥有\href{https://research.swtch.com/gophercount}{超过两百万开发者}。我是该组织的成员之一（共 163 人），目前负责维护 x/mobile 及相关构建器，同时还活跃向运行时及标准库提交贡献}
  \resumeSubItem{\href{http://github.com/fyne-io/fyne/}{fyne}（组织成员）}{fyne 是一个开源的 GUI 框架，我是组织的核心成员之一（共 12 人），主要关注在图形和移动端驱动以及性能改进。}
  \resumeSubItem{\href{https://golang.design}{golang.design}（创建者）}
  {我是组织的创建人，该组织目前发布了超过 25 款软件项目并共计 6 名成员。从 2020 年 9 月至今，已拥有超过 465k 访问次数和超过 66k 历史访问者。}
  \resumeSubItem{\href{https://talkgo.org}{Go 夜读}（组织成员）}
  {我是该组织的核心成员。 社区每周组织公开技术讲座，目前有 6.35k+ 订阅者，组织了 132 场公开讲座。 我贡献了 7 个演讲，它们是观看次数最多的演讲之一。}
  \resumeSubItem{\href{https://github.com/xitu/gold-miner}{掘金翻译社区}（组织成员）}
  {主要贡献者，将 50 多篇英文文章翻译成中文。}
  \resumeSubItem{其他贡献}{\href{http://github.com/tensorflow/tensorflow/}{Tensorflow} (164+ stars), \href{https://github.com/etcd-io/etcd}{etcd} (39.6k+ stars), etc.}
  \resumeSubHeadingListEnd
}