\ifthenelse{\boolean{en}} {
    \section{\textbf{Publications}}
}{
    \section{\textbf{出版物}}
}

\ifthenelse{\boolean{en}} {
  \subsection{Proceedings}
}{
  \subsection{会议论文集}
}

\resumeSubHeadingListStart
\listItem{
    \textbf{Changkun Ou}, Sven Mayer, Andreas Butz. 2023.
    \emph{The Impact of Expertise in the Loop for Exploring Machine Rationality}.
    To appear in the 28th ACM Symposium on Intelligent User Interface (IUI '23). ACM, New York, NY, USA, 15 pages.
}
\listItem{
    Francesco Chiossi, \textbf{Changkun Ou}, Sven Mayer. 2023.
    \emph{Exploring Physiological Correlates of Visual Complexity Adaptation: Insights from EEG, ECG, and EDA Data for Sensor Fusion Modelling in Virtual Reality Adaptive Systems}.
    Under review in the Extended Abstracts of the 2023 CHI Conference on Human Factors in Computing Systems (CHI EA '23). ACM, New York, NY, USA, 9 pages.
}
\listItem{
    Francesco Chiossi, Luke Haliburton, \textbf{Changkun Ou}, Andreas Butz, Albrecht Schmidt. 2023.
    \emph{Short-Form Videos Degrade Our Capacity to Retain Intentions: Effect of Context Switching On Prospective Memory}.
    In the 2023 ACM Conference on Human Computer Interaction (CHI'23). ACM, New York, NY, USA, 14 pages.
}
\listItem{
    Dennis Dietz, Carl Oechsner, \textbf{Changkun Ou}, Francesco Chiossi, Fabio Sarto, Sven Mayer, Andreas Butz. 2022.
    \emph{Walk This Beam: Impact of Different Balance Assistance Strategies and Height Exposure on Performance and Physiological Arousal in VR}.
    In 28th ACM Symposium on Virtual Reality Software and Technology (VRST '22). ACM, New York, NY, USA, Article 32, 12 pages. \faAward~\textbf{Best Paper Award}.
    \url{https://doi.org/10.1145/3562939.3567818}
}
\listItem{
    \textbf{Changkun Ou}, Daniel Buschek, Sven Mayer, Andreas Butz. 2022.
    \emph{The Human in the Infinite Loop: A Case Study on Revealing and Explaining Human-AI Interaction Loop Failures}.
    In Mensch und Computer 2022 (MuC'22). ACM, New York, NY, USA, 11 pages. \faAward~\textbf{Honorable Mention Award}.
    \url{https://doi.org/10.1145/3543758.3543761}
}
\listItem{
    \textbf{Changkun Ou}, Daniel Buschek, Malin Eiband, Andreas Butz. 2021.
    \emph{Modeling Web Browsing Behavior across Tabs and Websites with Tracking and Prediction on the Client Side}.
    arXiv preprint. 10 pages.
    \url{https://arxiv.org/abs/2103.04694}.
}
\listItem{
    Kai Holländer, Luca Schellenberg, \textbf{Changkun Ou}, and Andreas Butz. 2020.
    \emph{All Fun and Games: Obtaining Critical Pedestrian Behavior Data from an Online Simulation}.
    In Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems (CHI EA '20). ACM, New York, NY, USA, 9 pages.
    \url{https://doi.org/10.1145/3334480.3382797}
}
\listItem{
    \textbf{Changkun Ou}, Yifei Zhan, Yaxi Chen. 2019.
    \emph{Identifying Malicious Players in GWAP-based Disaster Monitoring Crowdsourcing System}.
    In the 2nd International Conference on Artificial Intelligence and Big Data (ICAIBD). IEEE. New York, NY, USA, 10 pages. \faAward~\textbf{Best Paper Award}.
    \url{https://doi.org/10.1109/ICAIBD.2019.8836972}
}
\resumeSubHeadingListEnd

\ifthenelse{\boolean{en}} {
  \subsection{Books}
}{
  \subsection{书籍}
}

\resumeSubHeadingListStart
\listItem{
    \textbf{Changkun Ou}. 2023.
    \emph{The Elements of Go: Under the Hood}.
    To appear in Posts \& Telecom Press.
    \url{https://golang.design/under-the-hood/}
}
\listItem{
    Quancheng Rao, \textbf{Changkun Ou}. 2022.
    \emph{The Handbook of Go Programming Interviews}.
    China Machine Press. ISBN: 9787111702429.
    \url{https://golang.design/go-questions}
}
\listItem{
    \textbf{Changkun Ou}. 2021.
    \emph{Modern C++ Tutorial: C++11/14/17/20 On the Fly}.
    In GitHub. 89 pages.
    \url{https://changkun.de/modern-cpp}
}
\resumeSubHeadingListEnd

\ifthenelse{\boolean{en}} {
  \subsection{Articles}
}{
  \subsection{文章}
}

\resumeSubHeadingListStart
\listItem{
    \textbf{Changkun Ou}. Sven Mayer, Daniel Buschek, Andreas Butz. 2024.
    \emph{Rethinking Opinion Measurement Interfaces for Human-in-the-Loop Optimization}.
    Under review in ACM Transactions on Computer-Human Interaction. ACM, New York, NY, USA, 28 pages.
}
\listItem{
    Yaxi Chen, \textbf{Changkun Ou}. 2016.
    \emph{Combining Touch Biometrics and Motion Sensors for Hand Posture Recognition and User Authentication System}.
    In Journal of Southwest University for Nationalities (Nature Science Edition). 7 pages.
    \url{https://doi.org/10.11920/xnmdzk.2016.04.011}
}
\listItem{
    Yaxi Chen, \textbf{Changkun Ou}, Zhaoyang Guo. 2014.
    \emph{Space interactions based on monocular vision and simple gestures}.
    In Journal of Southwest University for Nationalities (Natural Science Edition). 6 pages.
    \url{https://doi.org/10.3969/j.issn.1003-4271.2014.06.13}
}
\resumeSubHeadingListEnd

\ifthenelse{\boolean{en}} {
  \subsection{Technical Reports}
}{
  \subsection{技术报告}
}

\resumeSubHeadingListStart
\listItem{
  \textbf{Changkun Ou}. 2021.
  \emph{(Generic) Functional Options Pattern}.
  In the golang.design Research. 10 pages.
  \url{https://golang.design/research/generic-option.pdf}
}
\listItem{
  \textbf{Changkun Ou}. 2021.
  \emph{The Ultimate Channel Abstraction}.
  In the golang.design Research. 14 pages.
  \url{https://golang.design/research/ultimate-channel.pdf}
}
\listItem{
  \textbf{Changkun Ou}. 2021.
  \emph{A Concurrent-safe Centralized Pointer Managing Facility}.
  In the golang.design Research. 14 pages.
  \url{https://golang.design/research/cgo-handle.pdf}
}
\listItem{
  \textbf{Changkun Ou}. 2021.
  \emph{Scheduling Function Calls with Zero Allocation}.
  In the golang.design Research. 17 pages.
  \url{https://golang.design/research/zero-alloc-call-sched.pdf}
}
\listItem{
  \textbf{Changkun Ou}. 2020.
  \emph{Pointers Might Not be Ideal as Arguments}.
  In the golang.design Research. 10 pages.
  \url{https://golang.design/research/pointer-params.pdf}
}
\listItem{
  \textbf{Changkun Ou}. 2020.
  \emph{Eliminating A Source of Measurement Errors in Benchmarks}.
  In the golang.design Research. 10 pages.
  \url{https://golang.design/research/bench-time.pdf}
}
\resumeSubHeadingListEnd

\ifthenelse{\boolean{en}} {
  \subsection{Miscellaneous}
}{
  \subsection{其他}
}

\resumeSubHeadingListStart
\listItem{
  Julius Girbig, \textbf{Changkun Ou}, and Sylvia Rothe. 2022.
  \emph{Generative 3D Animation Pipelines: Automating Facial Retargeting Workflows}.
  In Workshop on ``AI-Generated Characters: Putting Deepfakes to Good Use'' of CHI '22: ACM CHI Conference on Human Factors in Computing Systems. New Orleans, LA, USA, 4 pages.
  \url{https://changkun.de/paper/deepfake.pdf}
}
\listItem{
    Jingyi Li, \textbf{Changkun Ou}, Yong Ma. 2019.
    \emph{Cultivation and Incentivization of HCI Research and Community in China: Taxonomy and Social Endorsements}.
    In Workshop on ``HCI in China: Research Agenda, Education Curriculum, Industry Partnership, and Communities Building'' of the 2020 CHI Conference on Human Factors in Computing Systems (CHI EA '19). Glasgow, UK, 7 pages.
    \url{https://changkun.de/paper/china.pdf}
}
\listItem{
    \textbf{Changkun Ou}. 2018.
    \emph{An Introduction to Recent Mobile Affective Inference Techniques: Methods, Applications and Challenges}.
    In Advanced Seminar Media Computer Science, LMU Munich. 9 pages.
    \url{https://changkun.de/paper/emotions.pdf}
}
\listItem{
    Matthias Geiger, \textbf{Changkun Ou}, Cedric Quintes. 2017.
    \emph{WatchOut: A Road Safety Extension for Pedestrians on a Public Windshield Display}.
    arXiv preprint. 5 pages.
    \url{https://arxiv.org/abs/1905.05390}
}
\listItem{
    \textbf{Changkun Ou}, Mu Huang, Mengxin Shi, Jiang Cheng. 2014.
    \emph{A Study in Keep-Right-Except-To-Pass Rule}.
    In the Mathematical Contest in Modeling. 35 pages. \faAward~\textbf{Meritorious Winner}
    \url{https://changkun.de/paper/keepright.pdf}
}
\resumeSubHeadingListEnd

\ifthenelse{\boolean{en}} {
  \subsection{Presentations}
}{
  \subsection{演讲}
}

\resumeSubHeadingListStart
\listItem{
  Changkun Ou. 2022.
  \emph{The Decision Maker's Dilemma: or how I stopped struggling with possible choices}.
  LMU Munich Internal Doctoral Colloquium. Chiemsee, Germany.
  \url{https://changkun.de/talk/dilemma.pdf}
}
\listItem{
  Changkun Ou. 2022.
  \emph{Generics in Go 1.18}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/generics118.pdf}
}
\listItem{
  Changkun Ou. 2022.
  \emph{What is A Rational Community Discussion?}
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/rational.pdf}
}
\listItem{
  Changkun Ou. 2021.
  \emph{Can we compute the free-will?}.
  LMU Munich Internal Doctoral Colloquium. Venice, Italy.
  \url{https://changkun.de/talk/polyred6fold.pdf}
}
\listItem{
  Changkun Ou. 2021.
  \emph{Delicate Dance: Preferences in Interactive Meshing}.
  LMU Munich Internal Doctoral Colloquium. Virtual Event.
  \url{https://changkun.de/talk/polyred5star.pdf}
}
\listItem{
  Changkun Ou. 2020.
  \emph{A Future of Polygon Reduction}.
  LMU Munich Internal Doctoral Colloquium. Venice, Italy.
  \url{https://changkun.de/talk/polyred4us.pdf}
}
\listItem{
  Changkun Ou. 2020.
  \emph{Reliable Benchmarking}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/gobench.pdf}
}
\listItem{
  Changkun Ou. 2020.
  \emph{Go 2 Generics? A (P)review}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/go2generics.pdf}
}
\listItem{
  Changkun Ou. 2020.
  \emph{A Study on Go Timer Implementation}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/timer.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Technological Outlook}.
  Lecture Online Multimedia. Munich.
  \url{https://changkun.de/talk/omm9.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Understanding Communicating Sequential Processes}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/csp.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Simplicity is complicated: On the balance of performance and knobs}.
  LMU Munich Internal Doctoral Colloquium. Vienna, Austria.
  \url{https://changkun.de/talk/polyred2what.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Real-world Go Concurrency Bugs}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/bug.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Internals of Channel and Select in Go}.
  The TalkGo Meetup. Virtual Event.
  \url{https://changkun.de/talk/channel.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Identifying Malicious Players in GWAP-based Disaster Monitoring Crowdsourcing System}.
  ICAIBD. Chengdu, China.
  \url{https://changkun.de/talk/gwap.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{A Glimpse to the Advances of Mesh Representation Learning}.
  Internal Doctoral Colloquium Spring. Bernried, Germany.
  \url{https://changkun.de/talk/polyred1step.pdf}
}
\listItem{
  Changkun Ou. 2019.
  \emph{Understanding and Predicting User Browsing Behavior}.
  Masters Defence Presentation. Munich, Germany.
  \url{https://changkun.de/talk/master.pdf}
}
\listItem{
  Changkun Ou. 2018.
  \emph{On the development of Quantified UX Metric}.
  Design Workshop II, LMU Munich. Munich, Germany
  \url{https://changkun.de/talk/qux.pdf}
}
\listItem{
  Changkun Ou. 2018.
  \emph{Capsule Network with Routing Mechanism}.
  Advanced Seminar Deep Learning, LMU Munich. Munich, Germany.
  \url{https://changkun.de/talk/capsnet1.pdf},
  \url{https://changkun.de/talk/capsnet2.pdf}
}
\listItem{
  Changkun Ou. 2018.
  \emph{Understanding Generalization in Deep Learning}.
  Advanced Seminar Deep Learning, LMU Munich. Munich, Germany.
  \url{https://changkun.de/talk/generalization.pdf}
}
\listItem{
  Hermann Redich, Patrick Börzel, Isabella Galter, Collin Leiber, Changkun Ou. 2018.
  \emph{Convolutional Neural Networks from Zero to Hero}.
  Advanced Seminar Deep Learning, LMU Munich. Munich, Germany.
  \url{https://changkun.de/talk/cnn.pdf}
}
\listItem{
    Changkun Ou. 2016.
    \emph{Mathematical Modeling Tutorial}.
    TouTube. Virtual Events.
    \url{https://changkun.de/s/playlist/math-modeling}
}
\resumeSubHeadingListEnd

\ifthenelse{\boolean{en}} {
  \subsection{Theses}
}{
  \subsection{毕业论文}
}

\resumeSubHeadingListStart
\listItem{
    \textbf{Changkun Ou}. 2019.
    \emph{Understanding and Predicting Web Browsing Behavior}.
    In the Institute of Computer Science. LMU Munich. 70 pages. \textbf{Master Thesis}.
    \url{https://changkun.de/thesis/master.pdf}
}
\listItem{
    \textbf{Changkun Ou}. 2016.
    \emph{Designing Alternative Contact-free Control Modalities for Smart Watches}.
    In the Institute of Computer Science and Engineering. Southwest University of Nationalities. 47 pages. \textbf{Bachelor Thesis}. \faAward~\textbf{Excellent Bachelor Thesis}.
    \url{https://changkun.de/thesis/bachelor.pdf}
}
\resumeSubHeadingListEnd
