\ifthenelse{\boolean{en}} {
\section{\textbf{Teaching Experience}}
}{
\section{\textbf{教学经历}}
}

\resumeSubHeadingListStartNoLabel
\resumeSubheading
{Lecture \href{http://www.medien.ifi.lmu.de/lehre/ss22/cg1/}{Computer Graphics}}{2020/2021/2022}
{
    \makecell[l]{As teaching assistant and instructor at LMU Munich. For B.Sc. students, approx. 200 students each year.\\Authored materials: \url{https://changkun.de/s/teach/cg}}
}{\makecell[r]{Summer\\~}}

\resumeSubheading
{Practical \href{https://www.medien.ifi.lmu.de/lehre/ws2122/gp/}{Geometry Processing}}{2020/2021}
{
    \makecell[l]{As lecturer and instructor at LMU Munich. For M.Sc. students, 6 students each year.\\
    Authored materials: \url{https://changkun.de/s/teach/gp}}
}{\makecell[r]{Winter\\~}}

\resumeSubheading
{Lecture \href{https://www.medien.ifi.lmu.de/lehre/ws2122/iv/}{Information Visualization}}{2021}
{
    \makecell[l]{As teaching assistant at LMU Munich. For M.Sc. students, approx. 100 students.\\
    Authored materials: \url{https://changkun.de/s/teach/iv}}
}{\makecell[r]{Winter\\~}}

\resumeSubheading
{Lecture \href{http://www.medien.ifi.lmu.de/lehre/ws1920/omm/}{Online Multimedia}}{2019}
{
    \makecell[l]{As teaching assistant and guest speaker at LMU Munich. For M.Sc. students, approx. 180 students.\\
    Authored materials: \url{https://changkun.de/s/teach/omm}}
}{\makecell[r]{Winter\\~}}

\resumeSubheading
{Seminar \href{http://www.medien.ifi.lmu.de/lehre/ws1920/hs/}{Advances in Computer Graphics}}{2019}
{As event organizer and supervisor at LMU Munich. For M.Sc. students, 6 students.}{Winter}

\resumeSubheading
{Seminar \href{http://www.medien.ifi.lmu.de/lehre/ws2122/hs/}{Advanced Media Informatics}}{2019/2021}
{As supervisor at LMU Munich}{Summer/Winter}

\resumeSubheading
{Lecture \href{http://www.dbs.ifi.lmu.de/cms/studium_lehre/lehre_master/deep1819/index.html}{Deep Learning and Artificial Intelligence}}{2018}
{
    \makecell[l]{As student tutor at LMU Munich.\\
    Authored manuscripts: \url{https://changkun.de/s/teach/dl}}
}{\makecell[r]{Winter\\~}}

\resumeSubheading
{Lecture \href{http://www.dbs.ifi.lmu.de/cms/studium_lehre/lehre_master/ml18/index.html}{Machine Learning}}{2018}
{
    \makecell[l]{As student tutor at LMU Munich.\\
    Authored manuscripts: \url{https://changkun.de/s/teach/ml}}
}{\makecell[r]{Summer\\~}}


\resumeSubheading
{Lecture Human-computer Interaction}{2015}
{As student tutor at Southwest University for Nationalities.}{Summer}


\resumeSubheading
{Theses/Seminars Supervision}{2020/2021/2022}
{As supervisor}{}
\resumeItemListStart
\resumeItem{Bachelor Thesis}{2022. Shiyi Gou. \emph{Exploring, Assisting, and Improving Human Rationality using Computational Approaches}.}
\resumeItem{Master Thesis}{2022. Johannes Merkt. \emph{Procedural Modeling with Nodes}.}
\resumeItem{Master Thesis}{2022. Kehong Deng. \emph{High Dimensional Trajectory Data Interpretation and Visualization}.}
\resumeItem{Bachelor Thesis}{2022. Nicolas Mogicato. \emph{On-the-fly Mesh Streaming}.}
\resumeItem{Bachelor Thesis}{2022. Benjamin Sühling. \emph{Mesh Repairing using Deep Networks}.}
\resumeItem{Bachelor Thesis}{2022. Zihan Kong. \emph{Real Time Ray Tracing using Generative AI}.}
\resumeItem{Bachelor Thesis}{2022. Gerhard van Nooy. \emph{PAppearance-preserving Mesh Processing in Hierarchical Networks}.}
\resumeItem{Master Thesis}{2021. Kevin Nsieyanji. \emph{Scheduling, Profiling and Optimizing Hybrid Renderer}.}
\resumeItem{Bachelor Thesis}{2021. Feng Chen. \emph{Exploiting Human Preferences with Reinforcement Learning Approaches}.}
\resumeItem{Master Seminar}{2021. Darina Cvetanova. \emph{Recent Advances in Neural Rendering for 3D Applications}.}
\resumeItem{Bachelor Thesis}{2021. Julius Girbig. \emph{Automated Facial Rig Registration for Motion Capture}. Cosupervision: Prof. Dr. Sylvia Rothe.}
\resumeItem{Bachelor Thesis}{2021. Oliver Möller. \emph{Web User Interface Optimization from Preferential Ratings}.}
\resumeItem{Bachelor Thesis}{2021. Christian Schmidt. \emph{Progressive BVH Refinement in Interactive Ray Tracing}.}
\resumeItem{Master Thesis}{2021. Elena Liebl. \emph{Evaluating Human Expertise in 3D Model Simplification}.}
\resumeItem{Master Thesis}{2021. Samuel Eiler. \emph{Meshless Neural Rendering}.}
\resumeItem{Master Seminar}{2020. Maksimilians Verbickis \emph{Understanding and Evaluating Human Preferences in 3D Modeling}.}
\resumeItem{Master Seminar}{2020. David Dodel, Ofek Lewinsohn. \emph{Geometric Processing in Learning}. Cosupervision: Dennis Dietz.}
\resumeItem{Master Seminar}{2020. Felix Dietz, Daniel Neumann. \emph{Reinforcement Learning in Physics-based Simulation}. Cosupervision: Dennis Dietz.}
\resumeItem{Master Seminar}{2020. Cecilia Thümmler. \emph{Human Perception and Preference in 3D Modelling}. }
\resumeItemListEnd
\resumeSubHeadingListEnd