\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color,xcolor}
\usepackage[
pdfauthor={Ou Changkun},
pdftitle={Resume},
pdfproducer={Ou Changkun}
pdfcreator={Ou Changkun},
pdfsubject={Ou Changkun Resume},
pdfkeywords={Resume, Ou Changkun},
]{hyperref}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\definecolor{linkcolor}{HTML}{00008B}
\definecolor{shade}{HTML}{D4D7FE}      %light blue shade
\definecolor{text1}{HTML}{000000}      %text is black
\definecolor{headings}{HTML}{00008B}   %navy blue
\hypersetup{colorlinks,breaklinks,
            urlcolor=linkcolor,
            linkcolor=linkcolor
}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{https://changkun.us/}{\Large Ou Changkun}} & +49 157 7214 1480 / +86 186 1322 5636\\
Munich, Germany                                      &  \href{mailto:hi@changkun.us}{hi@changkun.us}\\
\sffamily Last update: \today                           & \href{https://changkun.us/about}{changkun.us/about}
\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Munich}{Munich, Germany}
      {Master of Science in Human-Computer Interaction}{Oct. 2016 -- Present}
    \resumeSubheading
      {Southwest University for Nationalities}{Chengdu, China}
      {Bachelor of Engineering in Computer Science;  GPA: 3.74/4.0 (1/154)}{Sep. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://shiyanlou.com/}{Shiyanlou}}{Chengdu, China}
      {Software Engineer (Intern)}{Jun. 2016 -- Sep. 2016}
      \resumeItemListStart
        \resumeItem{shiyanlou-logsys}
          {Built \& maintained ELK+Redis distributed log analytics system;}
        \resumeItem{shiyanlou-desktop}
          {Developed a cross-platform Electron Windows/macOS/Linux desktop client;}
        \resumeItem{shiyanlou-recosys}
          {Developed a course recommendation system based on collaborative filtering through Python;}
        \resumeItem{shiyanlou-courses}
          {Wrote 17 course crash and advanced tutorials for C++ users.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Open Source Projects}
      {\href{https://github.com/changkun/}{github.com/changkun}}
  \resumeSubHeadingListEnd
%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages:}{ python; javascript; c; c++; objc; swift; markdown/pandoc; \LaTeX; Native Chinese Speaker; Professional Fluent English; Elementary German}
   }
   \item{
    \textbf{Systems/Tools:}{ Mac user; General Linux DevOps; Docker; AWS/DigitalOcean/Aliyun; SQL/MongoDB; zsh/tmux/vim/vscode}
   }
   \item{
    \textbf{Frameworks:}{ numpy/opencv/matplotlib/skearn/tensorflow, flask, jquery/react/vue/polymer/electron}
   }
   \item{
     \textbf{Knowledges:}{ 
       \resumeItemListStart
        \resumeItem{Human Side}
          { Human-Computer Interaction; User Study; User Experience; Human Computation; Social Psychology}
        \resumeItem{Machine Side}
          { Machine Learning; Recommendation System; Big Data Mining; Computer Vision; Distributed Computing; System Architecture}
        \resumeItem{Mathematics}
          { Functional Analysis; Stochastic Process; Analytic Number Theory}
      \resumeItemListEnd
     }
   }
 \resumeSubHeadingListEnd
%--------PUBLICATIONS------------
\section{Publications}
 \resumeSubHeadingListStart
   \item{
       Changkun Ou.
       The Fastest Guide of C++11/14. 
       2016, 
       \href{https://www.gitbook.com/book/changkun/cpp1x-tutorial/details}{Simplified Chinese}, 
       \href{https://github.com/changkun/cpp1x-tutorial}{Source Code}
   }
   \item{
       Changkun Ou, Yaxi Chen(responsible professor), Andreas Butz(co-reviwer).
       Designing Alternative Contact-free Control Modalities for Smart Watches. 
       2016, Bachelor Thesis. \href{https://changkun.us/files/cv/bachelor-thesis-cn.html}{Simplified Chinese}, 
       \href{https://changkun.us/files/cv/bachelor-thesis-en.html}{English}
   }
   \item{
       Changkun Ou.
       Mathematical Modeling Tutorial (Mandarin Chinese Video Series.
       2016, \href{https://www.youtube.com/watch?v=EUfXE3vP9_A&list=PLwUqqMt5en7c7iZIseCVAS5BX6RPkS-qR}{YouTube Playlist}
   }
   \item{
       Changkun Ou, Yaxi Chen. 
       Combining Touch Biometrics and Motion Sensors for Hand Posture Recognition and User Authentication System. 
       Journal of Southwest University for Nationalities(Nature Science Edition). 
       2016, 42(4):429-435. \href{https://changkun.us/files/cv/touch.swun.html}{Simplified Chinese}
   }
   \item{
       Changkun Ou, Zhaoyang Guo, Yaxi Chen.
       Space interactions based on monocular vision and simple gestures. 
       Journal of Southwest University for Nationalities(Natural Science Edition). 
       2014, 40(16):871-876. \href{https://changkun.us/files/cv/vision.swun.html}{Simplified Chinese}
   }
   \item{
       Changkun Ou, Mu Huang, Mengxin Shi, Jiang Cheng. 
       A Study in Keep-Right-Except-To-Pass Rule. 
       2014, MCM Meritorious Winner \href{https://changkun.us/files/cv/28922.public.html}{English}
   }
 \resumeSubHeadingListEnd
\end{document}