\section{\textbf{Selected Open Projects}}
  \resumeSubHeadingListStart

    \resumeSubItem{Open Source Projects}
    {\href{https://github.com/changkun/}{Homepage}}

    \resumeSubheading
      {TensorFlow Documentations Official Translations}{}
      {Management member, translator, proofreading. \href{https://github.com/xitu/tensorflow-docs}{Repository}}{Oct. 2017 -- Present}

    \resumeSubheading
      {Haggles}{}
      {Personal Kaggle solutions}{Nov. 2017 -- Present}
      \resumeItemListStart
        \resumeItem{Source Code}
          {\href{https://github.com/changkun/haggles}{Repository}}
      \resumeItemListEnd

    \resumeSubheading
      {Gitchain}{Munich, Germany}
      {Siemens AILab Hackathon 2nd Winner Project: Cryptocurrencies prediction}{Nov. 2017}
      \resumeItemListStart
        \resumeItem{Description}{Predict the success of a new cryptocurrency via its source code.}
        \resumeItem{Source Code}{\href{https://github.com/changkun/gitchain}{Repository}}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Echo Skill}{Munich, Germany}
      {Voice assistant}{Apr. 2017 - Aug. 2017}
      \resumeItemListStart
        \resumeItem{Description}{A voice assistant for english learner.}
        \resumeItem{Source Code}{\href{https://github.com/changkun/speak-alexa}{Repository}}
      \resumeItemListEnd

    \resumeSubheading
      {Smart Watches Contact-free Control Modalities}{Chengdu, China}
      {Bachelor Thesis}{Apr.2016 -- Jun.2016}
      \resumeItemListStart
        \resumeItem{Description}{Developed an alternative way -- midair gesture control -- to operate smart watches}
        \resumeItem{Source Code}{\href{https://github.com/changkun/BachelorThesis}{Repository}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd