\section{\textbf{Selected Publications}}
 \resumeSubHeadingListStart
    \item{
      Changkun Ou.
      \emph{Capsule Network with Routing Mechanism Part 2: Matrix Capsules}. Talk, 2018. \href{https://docs.google.com/presentation/d/1ccEsDtqjyQVvEvF-MDfwwnXqht5mPRE3c800vs5yJNY/edit?usp=sharing}{Slides}, \href{https://www.youtube.com/watch?v=akq6PNnkKY8}{Video}.
    }
    \item{
      Changkun Ou.
      \emph{Understanding Generalization in Deep Learning}.
      Advanced Seminar Deep Learning, IFI LMU, 2018. \href{https://docs.google.com/presentation/d/1eNUYH9_3bbBO7bONPU8BCTr2DOMC69gdOJvBgpLjwNg/edit?usp=sharing}{Slides}, \href{https://www.youtube.com/watch?v=z9je5YlnBgI&t=1585s}{Video}.
    }
    \item{
      Changkun Ou.
      \emph{Capsule Network with Routing Mechanism Part 1: Dynamic Routing}. Talk, 2018. \href{https://docs.google.com/presentation/d/1w5Ah406ufGu1M1iwly0e-QYFl3MMdHRK29LLibRB9HU/edit?usp=sharing}{Slides}, \href{https://www.youtube.com/watch?v=wC0rhjvst8I}{Video}.
    }
    \item{
      Hermann Redich, Patrick Börzel, Isabella Galter, Collin Leiber, Changkun Ou
      \emph{Convolutional Neural Networks from Zero to Hero}.
      Advanced Seminar Deep Learning, IFI LMU, 2018. \href{https://github.com/changkun/talks/blob/master/201712/cnn.pdf}{Slides}.
    }
    \item{
      Changkun Ou.
      \emph{An Introduction to Recent Mobile Affective Inference Techniques: Methods, Applications and Challenges}.
      Advanced Seminar Media Computer Science, IFI LMU, 2018. \href{https://github.com/changkun/hs-ws17-mobile-emotion-inference/blob/master/src/lmumihs-ou.pdf}{Paper}, \href{https://github.com/changkun/hs-ws17-mobile-emotion-inference/blob/master/slides/presentation-final.pdf}{Slides}.
    }
    \item{
      Changkun Ou.
      \emph{C++11/14/17 On the Fly: The Fastest Guide towards Modern C++}.
      Github Open Source Book, 2.8k+ Stars, 2018 \href{https://github.com/changkun/modern-cpp-tutorial}{English}, \href{https://github.com/changkun/modern-cpp-tutorial}{Chinese}.
    }
    \item{
      Changkun Ou, Yifei Zhan, Zhe Li.
      \emph{A Novel GWAP Disaster Monitoring System: Rating Model and Malicious Player Detection}.
      Lercture Human Computation, IFI LMU, 2017.
      \href{https://github.com/changkun/hc-ss17-disaster-monitoring/blob/master/report/hc_final_project_report_team_Hotpot.pdf}{English}
    }
   \item{
       Changkun Ou, Yaxi Chen(responsible professor), Andreas Butz(co-reviwer).
       \emph{Designing Alternative Contact-free Control Modalities for Smart Watches}. 
       2016, \textbf{Bachelor Thesis}. \href{https://changkun.us/files/cv/bachelor-thesis-cn.html}{Chinese}, 
       \href{https://changkun.us/files/cv/bachelor-thesis-en.html}{English}
   }
   \item{
       Changkun Ou, Yaxi Chen. 
       \emph{Combining Touch Biometrics and Motion Sensors for Hand Posture Recognition and User Authentication System}. 
       Journal of Southwest University for Nationalities(Nature Science Edition). 
       2016, 42(4):429-435. \href{https://changkun.us/files/cv/touch.swun.html}{Chinese}
   }
   \item{
       Changkun Ou, Zhaoyang Guo, Yaxi Chen.
       \emph{Space interactions based on monocular vision and simple gestures}. 
       Journal of Southwest University for Nationalities(Natural Science Edition). 
       2014, 40(16):871-876. \href{https://changkun.us/files/cv/vision.swun.html}{Chinese}
   }
   \item{
       Changkun Ou, Mu Huang, Mengxin Shi, Jiang Cheng. 
       \emph{A Study in Keep-Right-Except-To-Pass Rule}. 
       2014, American Mathematical Contest in Modeling Meritorious Winner. \href{https://changkun.us/files/cv/28922.public.html}{English}
   }
 \resumeSubHeadingListEnd