\section{\textbf{Selected Work Experiences}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Academic Tutor}{Munich, Germany}
      {LMU Lecture ``\href{http://www.dbs.ifi.lmu.de/cms/studium_lehre/lehre_master/ml18/index.html}{Machine Learning}'' SoSe 2018}{Aprl. 2018 -- Jul. 2018}
      \resumeItemListStart
      \resumeItem{Tutorial Notes}
          {\href{https://github.com/changkun/ss18-machine-learning-tutorial}{Repository}}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://labex.io/}{LabEx}}{Munich, Germany}
      {Backend Engineer}{Mar. 2018 -- Jul. 2018}
      \resumeItemListStart
      \resumeItem{Backend}
          {Automated Cloud Resource Access Management Microservices, Virtualization}
      \resumeItemListEnd
    \resumeSubheading
    {\href{https://magiclingua.com/}{MagicLingua}}{Munich, Germany}
    {Fullstack Engineer}{Nov. 2017 -- Mar. 2018}
    \resumeItemListStart
      \resumeItem{Speech Recognition}
        {Designing and implementing speech recognition solutions; Conversation Design; Answers Fault-tolerance; Audio Streaming Solutions}
      \resumeItem{General Development}
        {Angular; Spring; WebSocket; MongoDB; Elasticsearch; Serverless}
    \resumeItemListEnd
    \resumeSubheading
      {\href{http://www.medien.ifi.lmu.de}{LMU Media Informatics Group}}{Munich, Germany}
      {Student Researcher}{Oct. 2016 -- Jan. 2016}
      \resumeItemListStart
        \resumeItem{Research topic}
          {Combining motion sensors and touch offset classify hand Posture and users}
        \resumeItem{Outcomes}
          {A iOS prototype App for User Study, densely data analysis via Support Vector Machine; Paper report}
      \resumeItemListEnd
  \resumeSubHeadingListEnd