\section{\textbf{Selected Public Activities}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Juejin Translation Project}{\href{https://github.com/xitu/gold-miner}{GitHub}}
      {Translator, articles translation from English to Chinese}{since Apr. 2017}
      \resumeItemListStart
        \resumeItem{Translation}
          {\href{https://juejin.im/post/5937a61f2f301e006b2879a9}{How to build complex user interfaces without going completely insane}}
        \resumeItem{Proofreading}
          {\href{https://github.com/xitu/gold-miner/pull/1603}{Everyone is a designer. Get over it.}}
        \resumeItem{Translation}
          {\href{https://juejin.im/post/5915880b570c35006932fac9}{How to pretend you’re a great designer}}
      \resumeItemListEnd
    
    \resumeSubheading
      {Personal Translation}{}
      {Translation from English to Chinese}{since May 2016}
      \resumeItemListStart
        \resumeItem{\href{https://github.com/changkun/LeapDocCN}{Leap Motion Official Development Documentation Translation}}
          {full translation}
        \resumeItem{\href{http://swift.gg/2016/05/18/api-design-guidelines/}{Swift 3 API Design Guidelines}}
          {full translation}
        \resumeItem{\href{https://github.com/numbbbbb/the-swift-programming-language-in-chinese}{The Swift Programming Language Chinese Translation}}
          {responsible for Release Changes chapter}
      \resumeItemListEnd

    \resumeSubheading
        {Academic Tutor}{Chengdu, China}
        {Cooperation lecture “Human-Computer Interaction I” between LMU and SWUN}{Jul. 2015}

    \resumeSubheading
        {Student Volunteer}{Chengdu, China}
        {for Conference Smart Graphics 2015}{Aug. 2015}

    \resumeSubheading
        {SWUN Guigu Lab Team Leader}{Chengdu, China}
        {Tutorial for members applying projects}{Sep. 2014 -- Jun. 2015}

    \resumeSubheading
        {Mathematical Modeling Association Academic Vice Director}{Chengdu, China}
        {Academic tutorial for new members}{Oct. 2012 -- Jun. 2014}

    \resumeSubheading
        {Computer Application and Development Association Core Member}{Chengdu, China}
        {Programming tutorial for new members}{Oct. 2012 -- Dec. 2013}

    \resumeSubheading
        {SWUN Organization federation Excutive Member}{Chengdu, China}
        {Design \& Organization}{Oct. 2012 -- Jun. 2013}
  \resumeSubHeadingListEnd