\section{\textbf{Honors \& Awards}}
  \resumeSubHeadingListStart
  \resumeSubheading
        {Siemens AILab Hackathon}{Munich, Germany}
        {Second Winner}{Nov. 2017}
    \resumeSubheading
        {App@Night 2016 hackthon at University of Munich}{Munich, Germany}
        {IBM IoT team Successful Participant}{Nov. 2016}
    \resumeSubheading
        {hackaTUM at Technical University of Munich}{Munich, Germany}
        {Landeshauptstadt Muenchen Successful Participant}{Nov. 2016}
    \resumeSubheading
        {China National Scholarship}{Chengdu, China}
        {At UESTC}{Sep. 2016}
    \resumeSubheading
        {SWUN Bachelor Graduation Thesis Award}{Chengdu, China}
        {Excellent Thesis}{Jun. 2016}
    \resumeSubheading
        {Sichuan Province University Graduates Award}{Chengdu, China}
        {Outstanding Student}{Jan. 2016}
    \resumeSubheading
        {First-class Scholarship}{Chengdu, China}
        {SWUN Outstanding Student}{Nov. 2015}
    \resumeSubheading
        {SWUN College Student-Innovative Activity 2014}{Chengdu, China}
        {Annual Excellent Project}{Jun. 2015}
    \resumeSubheading
        {The National College Student-Innovative Projects}{Chengdu, China}
        {Concluding Certificate}{Jun. 2015}
    \resumeSubheading
        {Sichuan Computer Production Competition}{Chengdu, China}
        {2nd Award}{May 2015}
    \resumeSubheading
        {First-class Scholarship}{Chengdu, China}
        {SWUN Outstanding Student}{Nov. 2014}
    \resumeSubheading
        {China National Scholarship}{Chengdu, China}
        {At SWUN}{Sep. 2014}
    \resumeSubheading
        {Sichuan Computer Production Competition}{Chengdu, China}
        {2nd Award}{Jun. 2014}
    \resumeSubheading
        {Mathematical Contest in Modeling(MCM) 2014}{Chengdu, China}
        {Meritorious Winner}{Apr. 2014}
    \resumeSubheading
        {First-class Scholarship}{Chengdu, China}
        {SWUN Outstanding Student}{Nov. 2013}
    \resumeSubheading
        {Mathematical Contest in Modeling(MCM) 2013}{Chengdu, China}
        {Successful Participant}{Apr. 2013}
  \resumeSubHeadingListEnd